---
title: "RCovid19"
author: "SB"
date: "21/07/2020"
output:
  ioslides_presentation: default
  slidy_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Introdcution


- A new coronavirus designated 2019-nCoV was first identified in Wuhan, the capital of China's Hubei province.
- People developed pneumonia without a clear cause and for which existing vaccines or treatments were not effective.
- The virus has shown evidence of human-to-human transmission
Transmission rate (rate of infection) appeared to escalate in mid-January 2020 


The app explores the <a href="https://www.kaggle.com/imdevskp/corona-virus-report">dataset</a> to analyze the top 10 countries affected by the pandemic .



## Global Toll

In this slide,we get a glance of the dataset where we display the various variables available.

```{r, echo = TRUE}
covidata <- read.csv('C:/Users/HP/Desktop/DSCoursera/covid_19.csv')

head(covidata[,1:5],5)
```

## App Demo
The app displays the top 10 countries(in the form of a barplot) according to the variable chosen by the user,which may be **Active**,**Confirmed**,**Recovered** or **Deaths** 

```{r,echo=FALSE,warning=FALSE,message=FALSE}
recIdx <- order(-covidata[,"Recovered"],covidata[,"Country.Region"])
rec <- covidata[recIdx,c(1,4),drop = FALSE]
rec <- rec[1:10,]

par(mfrow=c(1,1))
    barplot(rec$Recovered,main="Countries by Recovered",space=0.1,width=1,las=3,names.arg = rec$Country.Region,col=rainbow(20),horiz=FALSE)
    axis(2,at= seq(0,1500000,200000))



```



## Future Scope


- The app can be further enhanced to add chloropleth maps,scatterplots,etc. 
- The varied amount of data available can be further used to fit regression models to explore various patterns from the data.
- For source code,visit https://github.com/kishibe-rohan/RCovid19